---
title: "Group 4 - Salary Prediction"
author: "Akash Gobalarajah, Cyril Alain Scheurmann, Keijo Alexander Nierula, Roman Krass"
date: "2024.03.14"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE, echo=FALSE}
# Getting started by changing the default output of echo to TRUE for the current document 
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)

# Create a list of packages to install and load into the work space
libraries = c("readr", "tidyverse", "dlookr", "ggplot2", "xgboost", "dplyr")
 
# Install packages from the predefined libraries list
lapply(libraries, function(x) if (!(x %in% installed.packages())) {
  install.packages(x)
})

# Load libraries
lapply(libraries, library, quietly = TRUE, character.only = TRUE)

# Remove current environment 
rm(list=ls())

#scientific notation: off
options(scipen=999) 
```

# Project Setup {.unnumbered}

```{r importData}
# Set seed
set.seed(7)

# Importing data
load("data_wage.RData")
salaryData <- data

```

# Checking data for NA values {.unnumbered}
In this part we check our data for missing values. This is important because missing values can cause problems in the analysis and can lead to wrong results. 

<details>
<summary>Click to expand NA results</summary>


```{r naValues, out.width = "100%"}

# Check for missing values in each column of the data set and store the result in the "has_NAs" data frame
has_NAs = as.data.frame(apply(data, 2, function(x) any(is.na(x))))

# Map matching column names for a more readable output
colnames(has_NAs) = c("has_NA")

# Print the has_NAs data frame to check if there are any NA values in our data set
has_NAs

```
</details>
As we can see from the output above none of the columns contain any missing values. This is very good so we don't have to deal with the problem of missing values.


# Data description

``` {r}
dim(data)

```
The `dim` function shows us, that we have 10'809 and 78 variables in our data set.

<details>
<summary>Click to expand to see data structure</summary>

```{r scructure}

# Check the structure of the data
str(data)

```
</details>
  
<details>
<summary>Click to expand to see the summary of all variables</summary>

```{r summary()}

# Check the summary of the data
summary(data)

```
</details>
When we look at the summary the variable `wage` has a minimum value of 0 and a maximum value of 551'774. This is a very big range and we have to check if there are any outliers in the data set. The big range can also be caused the dataset includes data from students to experts which indeed can have a big range in their salary.
All other variables look good. This is because a lot of variables are categorical variables which were one hot encoded. 

## How many numeric and how many categorical variables are included in the data? What categorical variable has the most levels in it?

```{r}
num_vars <- sum(sapply(data, is.numeric))
cat_vars <- sum(sapply(data, is.factor))

# Print counts
cat("Number of numeric variables:", num_vars, "\n")
cat("Number of categorical variables:", cat_vars, "\n")
```

Reporting the structure of the data set shows us, that we have `r as.character(cat_vars)` character columns and `r as.character(num_vars)` number columns.
Because we have `r as.character(cat_vars)` we cannot use all models because they only work with numeric data. If we could like to use a model like XGBoost we have to encode these categorical variables with one hot encoding so we end with only numeric variables.

Eventuell noch `diagnose` benutzen

## Check dependent variable wage

```{r}
# Plot histogram of wage
ggplot(data, aes(x = wage)) +
  geom_histogram(bins = 60, fill = "lightblue", color = "black") +
  scale_x_continuous(breaks = seq(min(data$wage), max(data$wage), by = 50000)) +
  labs(title = "Histogram of wage", x = "Wage", y = "Frequency") +
  theme_minimal(base_size = 17)

```

Wehen we look at the histogram of the wage we can see that that most of the values are between 0 and 150'000. There are also some values between 150'000 and 250'000. The values above 250'000 are very rare. This is also a bit as expected because wages above 200'000 are not so common as wages to 150'000.